On the assessment of the ability of measurements, nowcasts, and forecasts to track changes

### 2024-10-20 202410-rebuttal/main.tex
Fix typos, update rebuttal

\documentclass[12pt]{journalrebuttal}
\title{On the assessment of the ability of measurements, nowcasts, and forecasts to track changes}
\author{Jonas Rieger*, Bolin Liu, Bernd Saugel, Oliver Grothe}
% TODO Authors anpassen
\journal{BMC Medical Research Methodology}
\manuscriptid{304c3895-aec8-4c97-867a-23905ca7f85d}

@@

\begin{revcomment}
The literature review seems a little thin on references to concordance metrics for forecasts. It seems that references 21, 34, and 35 are the only one, but I am sure there are more out there.
\end{revcomment}
\begin{response}
    Thank you for sharing this observation. In response, we have expanded the number of references related to concordance metrics for forecasts, providing a more thorough overview of the current state of research in this area.
\end{response}

>>>>

\documentclass[12pt]{journalrebuttal}
\title{On the assessment of the ability of measurements, nowcasts, and forecasts to track changes}
\author{Jonas Rieger*, Bolin Liu, Bernd Saugel, Oliver Grothe}
\journal{BMC Medical Research Methodology}
\manuscriptid{304c3895-aec8-4c97-867a-23905ca7f85d}

@@

\begin{revcomment}
The literature review seems a little thin on references to concordance metrics for forecasts. It seems that references 21, 34, and 35 are the only one, but I am sure there are more out there.
\end{revcomment}
\begin{response}
    Thank you for sharing this observation. In response, we have expanded the number of references related to concordance metrics for forecasts in the introduction, providing a more thorough overview of the current state of research in this area.
\end{response}

### 2024-10-20 paper.tex
Fix typos, update rebuttal

In forecasting and nowcasting the evaluation of performance or goodness is usually based on statistical methods quantifying the accuracy such as the \ac{rmse}, probabilistic scoring rules, and calibration measures~\citep{Gneiting2007, Gunther2021, Wolffram2023}, see also~\citep{SteyerbergEwoutW.2010AtPo} for an overview in the medical context together with less known measures.
However, although techniques like ROC curves for binary direction models or more general concordance measures (e.g., \citep{Goenen2005}) are used, there is no general measure directly framed to assesses the method's \ac{atc}.
In a forecasting competition on armed conflicts, the assessment of the \ac{atc} recently gained attention as \citet{Vesco2022} proposed the novel \ac{tadda} score with an additive tracking-changes-component for evaluation.
However, the score poses an unintuitive incentive to forecasters and is thus theoretically problematic~\parencite{Bracher2023}.
When evaluating the performance or goodness of a measurement method like in classical mathod comparation studies, comparative statistics such as Bland-Altman analysis~\citep{Bland1986} and the percentage error \parencite{Critchley1999} are commonly used. In this strand of literature,  the best way to assess the \ac{atc} of measurement methods is a field of active ongoing research~\citep{Critchley20101180, CRITCHLEY2011536, Saugel2015, Saugel2018, Hiraishi2021}.

>>>>

In forecasting and nowcasting the evaluation of performance or goodness is usually based on statistical methods quantifying the accuracy such as the \ac{rmse}, probabilistic scoring rules, and calibration measures~\citep{Gneiting2007, Gunther2021, Wolffram2023}, see also~\citet{SteyerbergEwoutW.2010AtPo} for an overview in the medical context together with less known measures.
However, although techniques like ROC curves for binary direction models or more general concordance measures \citep[see, e.g., ][]{Goenen2005} are used, there is no general measure directly framed to assess the method's \ac{atc}.
In a forecasting competition on armed conflicts, the assessment of the \ac{atc} recently gained attention as \citet{Vesco2022} proposed the novel \ac{tadda} score with an additive tracking-changes-component for evaluation.
However, the score poses an unintuitive incentive to forecasters and is thus theoretically problematic~\parencite{Bracher2023}.
When evaluating the performance or goodness of a measurement method like in classical method comparison studies, comparative statistics such as Bland-Altman analysis~\citep{Bland1986} and the percentage error \parencite{Critchley1999} are commonly used. In this strand of literature, the best way to assess the \ac{atc} of measurement methods is a field of active ongoing research~\citep{Critchley20101180, CRITCHLEY2011536, Saugel2015, Saugel2018, Hiraishi2021}.
